Labor Market Income and Substitution Effects Explain Contemporary Natural Selection

### 2020-12-21 why-natural-selection.Rmd
tweaks

Figure \@ref(fig:plot-siblings-townsend) plots effects on *n siblings* by
Townsend deprivation quintile of birth area.

@@

ineq_comp %>% 
      select(
        PGS                 = score, 
        `Without selection` = diff_hypoth,
        `With selection`    = diff_children, 
        `% change`          = pct_change
      ) %>% 
      mutate(
        PGS = pretty_names(PGS)
      ) %>% 
      arrange(desc(`% change`)) %>% 
      as_hux() %>% 
      set_align(everywhere, -1, "right") %>% 
      set_number_format(everywhere, 2:3, 3) %>% 
      set_number_format(everywhere, 4, 1) %>% 
      set_caption("Differences in polygenic scores between highest and lowest income group.") %>% 
      set_width(0.6) %>% 
      theme_compact() %>% 
      set_bottom_border(final(1), everywhere)
```

>>>>

Figure \@ref(fig:plot-siblings-townsend) plots effects on *number of siblings* by
Townsend deprivation quintile of birth area.

@@

ineq_comp %>% 
      select(
        PGS                 = score, 
        `Without selection` = diff_hypoth,
        `With selection`    = diff_children, 
        `% change`          = pct_change
      ) %>% 
      mutate(
        PGS = pretty_names(PGS)
      ) %>% 
      arrange(desc(`% change`)) %>% 
      as_hux() %>% 
      set_align(everywhere, -1, "right") %>% 
      set_number_format(everywhere, 2:3, 3) %>% 
      set_number_format(everywhere, 4, 1) %>% 
      set_caption("Differences in polygenic scores between highest and lowest income group.") %>% 
      theme_compact() %>% 
      set_width(0.9) %>% 
      set_col_width(c(.35, .15, .15 , .15)) %>% 
      set_bottom_border(final(1), everywhere)
```
